### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@642638bfc147d135a1075a90473a98c2a061f374 🚀

Bats are important reservoir hosts for different classes of
microorganisms (Chu 2008, Donaldson 2010, Li 2010), some of which can
threaten human health. Chiropterans emerged around 64 million years ago
and are one of the most diverse mammalian orders, with an estimated
richness of more than 12000 species, (Peixoto F et al, 2018) and 14325
known species (Simmons \& Cirranello). They exhibit a broad variety of
habitat use, behaviour, and feeding strategies, resulting in their
playing an essential role in the delivery of several ecosystem services
tied to important ecosystem-derived benefits (Kasso 2013). For example,
over two-thirds of bats are know to be either obligate or facultative
insectivorous mammals, therefore playing an important role in the
regulation of insect pests that can affect crops (Williams-Guillen
2011), and vectors of diseases that put a risk on human health
(Gonsalves 2013). Because bats are globally distributed and have a long
evolutionary history, phylogeographic and biogeographic approaches are
required to shed light on the extant distribution of coevolutionary
processes between bats and the pathogens they carry. Not all areas in
which bats, viruses, and human are co-occuring are facing a risk of
spillover towards human populations, and the areas in which this risk
exist may not be facing risks of the same nature and magnitude.

@@

@@

@@

>>>>

Bats are important reservoir hosts for different classes of
microorganisms (Chu 2008, Donaldson 2010, Li 2010), some of which can
threaten human health. Chiropterans emerged around 64 million years ago
and are one of the most diverse mammalian orders, with an estimated
richness of more than 12000 species, (Peixoto et al. 2018) and 14325
known species (Simmons and Cirranello 2020). They exhibit a broad
variety of habitat use, behaviour, and feeding strategies, resulting in
their playing an essential role in the delivery of several ecosystem
services tied to important ecosystem-derived benefits (Kasso and
Balakrishnan 2013). For example, over two-thirds of bats are know to be
either obligate or facultative insectivorous mammals, therefore playing
an important role in the regulation of insect pests that can affect
crops (Williams-Guillén et al. 2008, Voigt and Kingston 2016), and
vectors of diseases that put a risk on human health (Gonsalves et al.
2013a, b). Because bats are globally distributed and have a long
evolutionary history, phylogeographic and biogeographic approaches are
required to shed light on the extant distribution of coevolutionary
processes between bats and the pathogens they carry. Not all areas in
which bats, viruses, and human are co-occuring are facing a risk of
spillover towards human populations, and the areas in which this risk
exist may not be facing risks of the same nature and magnitude.

@@

\leavevmode\hypertarget{ref-Gonsalves2013MosInf}{}%
Gonsalves, L. et al. 2013a. Do mosquitoes influence bat activity in
coastal habitats? - Wildlife Research 40: 10--24.

\leavevmode\hypertarget{ref-Gonsalves2013MosCon}{}%
Gonsalves, L. et al. 2013b. Mosquito Consumption by Insectivorous Bats:
Does Size Matter? - PLOS ONE 8: e77183.

\leavevmode\hypertarget{ref-Kasso2013EcoEco}{}%
Kasso, M. and Balakrishnan, M. 2013. Ecological and Economic Importance
of Bats (Order Chiroptera). - ISRN Biodiversity 2013: e187415.

@@

\leavevmode\hypertarget{ref-Peixoto2018SynEco}{}%
Peixoto, F. P. et al. 2018. A synthesis of ecological and evolutionary
determinants of bat diversity across spatial scales. - BMC ecology 18:
18.

@@

\leavevmode\hypertarget{ref-Simmons2020BatSpe}{}%
Simmons, N. B. and Cirranello, A. L. 2020. Bat Species of the World: A
taxonomic and geographic database.

\leavevmode\hypertarget{ref-Voigt2016BatAnt}{}%
2016. Bats in the Anthropocene: Conservation of Bats in a Changing World
(CC Voigt and T Kingston, Eds.). - Springer International Publishing.

\leavevmode\hypertarget{ref-Williams-Guillen2008BatLim}{}%
Williams-Guillén, K. et al. 2008. Bats Limit Insects in a Neotropical
Agroforestry System. - Science 320: 70--70.
